---
title: "Data Visualisation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(kableExtra)
source(here("scripts", "Experiment 1.R"))
source(here("scripts", "Experiment 2a.R"))
source(here("scripts", "Experiment 2b.R"))
source(here("scripts", "Experiment 3.R"))
```



## Experiment 1

### Egg counting 

```{r echo=FALSE, message=FALSE, warning=FALSE}

egg_counting1_plot 

```

#### The number of eggs laid by female flies across 4 diets

### Feeding behaviour 

```{r echo=FALSE, message=FALSE, warning=FALSE}

exp1_femaleall_plot + exp1_maleall_plot

```

#### The mean average number of flies feeding on diets across 2 days, females (shown in red) and males (shown in green)

### Not feeding 

```{r echo=FALSE, message=FALSE, warning=FALSE}

female_notfeedinge1_plot + male_notfeedinge1_plot

```

#### The mean average number of flies NOT feeding on diets across 2 days, females (shown in red) and males (shown in green)


## Experiment 2a

### Egg counting 

```{r echo=FALSE, message=FALSE, warning=FALSE}

mated_females_e2_eggcount_plot + virgin_female_e2_eggcount_plot

```

#### The mean average of eggs across four diet ratios with mated females (shown in red) and virgin females (shown in purple)


### Feeding behaviour 

```{r echo=FALSE, message=FALSE, warning=FALSE}

exp2matedall_plot + exp2avirginall_plot

```

#### The mean average number of flies feeding on diets across 3 days, mated females (shown in red) and virgin females (shown in pink)


## Experiment 2b

## Offspring count 
# -- 

### Feeding behaviour 

```{r echo=FALSE, message=FALSE, warning=FALSE}

exp2bmatedall_plot + exp2bvirginall_plot

```

#### The mean average number of flies feeding on diets across 2 days, mated females (shown in red) and virgin females (shown in pink)

## Experiment 3

## Offspring count 
# -- 

### Feeding behaviour 

```{r echo=FALSE, message=FALSE, warning=FALSE}

exp3femalesall_plot + exp3both_plot

```

#### The calculated proportional value of the mean average number of flies feeding on diets across 2 days, just mated females alone on a plate (shown in red) and mated females along with males on a plate (shown in purple)
