---
title: "R Notebook"
output: html_notebook
---


- Experiment 3 - 
 notes - think of this as a lab notebook for your analysis, write notes, thoughts and process here, run code in chunks

Testing the summary function to look at a poisson glm test 
```{r}
summary(exp3allglm1)
```


QUESTION 1: 

If I have a model which is poisson
Do I 
still use drop1 and let it be quasi-poisson 
or 
just use summary to see if a variable is significant. 



Checking performance for both of the models 
```{r}
performance::check_model(exp3alllm2)
```

```{r}
performance::check_model(exp3alllm2, check=c("qq"))
```



```{r}
performance::check_model(exp3allglm2)
```

```{r}
performance::check_model(exp3allglm2, check=c("qq"))
```

Th performance check for the linear model shows the homogenity of variance points to be very close together 
The performance check for the generalised linear model shows the homogenity of variance points to be further apart. 
Hence, for the homogenity of variance; the generalized linear model is better to follow. 

For the normality of residuals for the linear model isn't great. Especially at -2, to -2 points. 
The normality of residuals for the generalized linear model doesn't differ much from that of the linear model. 

The performance shows none of the models are great, but the generalized linear model is slighlty better, and also complex? 
I could go into using more complex models but it is best to stop here as there is very little difference between the ones that have been tried. 





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

